%Building
\documentclass[11pt]{article}

\usepackage[english]{babel}
\usepackage[margin=1in]{geometry}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

% Math/Greek packages
\usepackage{amssymb, amsmath, amsthm, mathtools, esint} 
\usepackage{algorithm, algorithmic}
\usepackage{upgreek}
\usepackage{physics}

% Graphics/Presentation packages
\usepackage{graphicx}
\usepackage{multirow, subcaption, cleveref}
\usepackage{tabulary, enumitem}
\usepackage{cancel}
\usepackage{float}	% better float control. Using the placement [H] instead of [!ht] for figures
\usepackage{longtable}

%replace "ref" with "cref", "Cref", "crefrange"

% Misc packages
\renewcommand\qedsymbol{\textit{``Quack"}} %change the QED symbol to ``Quack" for the inside joke of Quantum Entangled Ducks

% defining where the images are
\graphicspath{ {../ESOF 322 Project (drive copy)/} }


% suppress badbox
\hbadness=10000
\hfuzz=\maxdimen
\newcount\hbadness
\newdimen\hfuzz


%\usepackage{fontspec}
% Use this line to change the font of your file. If you have the Open Dyslexic v. 1 downloaded (bold-italic- bolditalics included), you can use this line. This font addresses Dyslexic people. 
%\setmainfont{OpenDyslexic}
% Use this line to change the font of your file. If you have the Atkinson Hyperlegible downloaded (bold-italic- bolditalics included), you can use this line. This font addresses sight-impaired peoples
 %\setmainfont{Atkinson Hyperlegible}

\begin{document}

\title{ESOF 322: Project 2 - Camp Management System; Test Plan}
\author{Jacob Coleman, William Jardee, Fletcher Philips, Megan Steinmasel}
\maketitle


%%TO-DO intro structure
%		user stories
%		use cases


\section*{Test Plan}

This is the Test Plan for the Camp Management System provided. Since there are 13 usecases, we have opted to only write test plans for eight of them; two by each group member. All relevant information about the usecases can be see in \cref{appendix:camp_sys}, and to increase readability the summary for each test case explains how it is related to the requirement and there is a link to the relevant use case/requirement(s).

\subsection*{Introduction}
The Camp Management System aims to serve as the connecting force that organizes how counselors, parents, and campers communicate information. The main structure of the system can be boiled down into four requirements:
\begin{enumerate}
	\item A way to track attendance,
	\item View Camper information,
	\item Create and view schedule, and
	\item Send a message to parents.
\end{enumerate}
The small subset of testing we show here will all be done using Functional Black-Box testing. That is, only testing that the the transformation of ``Input $\mapsto$ Output" is correct. The main testing techniques used are:
\begin{enumerate}
	\item Equivalence Partitioning (TC03: \cref{TC03}, TC04: \cref{TC04}, TC05: \cref{TC05}, TC06: \cref{TC06}, TC07: \cref{TC07}, TC08: \cref{TC08}),
	\item Boundary Value Analysis (TC04: \cref{TC04}, TC05: \cref{TC05}, TC06: \cref{TC06}),
	\item Decision Table Testing (TC01: \cref{TC01}, TC02: \cref{TC02}, TC06: \cref{TC06})
	\item State Transition Testing (TC04: \cref{TC04}), and
	\item Error Guessing  (TC03: \cref{TC03}, TC05: \cref{TC05}, TC06: \cref{TC06}, TC08: \cref{TC08}).
\end{enumerate}

% add intro, objectives, features, technique

\clearpage

%------------------------------------
% Fletcher's Test Cases
%------------------------------------
\subsection*{Test Suite 1: Messaging System}

\begin{table}[H]
\begin{center}
\caption{TC01}
\label{TC01}
\begin{tabular}{p{0.20\linewidth}p{0.70\linewidth}}
	ID: & TC01\\\hline
	Name: & Message Camp \\\hline
	Author: & Fletcher Phillips\\\hline
	Summary: &  Parents must be able to message the camp system through three routes: Text, Email, and an In-app messaging system. These all need to be tested individually.\\\hline
	Related \hspace{5em} Requirements:& Message Camp (\cref{des:message camp}); \hyperlink{Req4}{Req 4} \\\hline
	Preconditions:& \begin{enumerate}[topsep=0pt]
		\item Parent has a device to send a message (text, email, in-app messaging).
		\item Parent's contact information is in the system.
	\end{enumerate}\\\hline
	Test Script/ Procedure: & \begin{enumerate}[topsep=0pt]
		\item Choose messaging system.
		\item Create message to send.
		\item Send message.
		\item Confirmation receipt is sent.
	\end{enumerate}\\\hline
	Test Data & 
\end{tabular}
\end{center}
\end{table}

\begin{center}
\begin{longtable}{|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|}
	\hline 
	Test Case \# & Messaging System & Expected Result & Summary\\\hline
	TC01-01 & Text & Text message received by counselor or staff member and a confirmation receipt is received. & Verifies the camp staff member receives a parent's message via text.\vspace*{1em}\\\hline
	TC01-02 & Email & Email message received by counselor or staff member and a confirmation receipt is received. & Verifies the camp staff member receives a parent's message via email.\vspace*{1em}\\	\hline
	TC01-03 & In-app messaging & In-app message message irs received by counselor or staff member and a confirmation receipt is received. & Verifies the camp staff member.\vspace*{1em}\\\hline
\end{longtable}
\end{center}
\clearpage


\begin{table}[H]
\begin{center}
\caption{TC02}
\label{TC02}
\begin{tabular}{p{0.20\linewidth}p{0.70\linewidth}}
	ID: & TC02\\\hline
	Name: & Message Parent \\\hline
	Author: & Fletcher Phillips\\\hline
	Summary: &  The camp system must be able to message the parents through three routes: Text, Email, and an In-app messaging system. These routes are how the parent receives the message. All messaging is done through the system. These all need to be tested individually.\\\hline
	Related \hspace{5em} & Message Parent (\cref{des:message parent}); \hyperlink{Req4}{Req 4} \\\hline
	Preconditions:& \begin{enumerate}[topsep=0pt] 
		\item Parent's contact information is stored.
		\item Parent has created a profile.
	\end{enumerate}\\\hline
	Test Script/ Procedure: & \begin{enumerate}[topsep=0pt]
		\item Choose messaging system.
		\item Create the message.
		\item Send Message
	\end{enumerate}\\\hline
	Test Data &
\end{tabular}
\end{center}
\end{table}

\begin{center}
\begin{longtable}{|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|}
	\hline
	Test Case \# & Messaging System & Expected Result & Summary\\\hline
	TC02-01 & Text & Text message received by counselor or staff member and a confirmation receipt is received. & Verifies the camp staff member receives a parent's message via text.\vspace*{1em}\\\hline
	TC02-02 & Email & Email mesage received by counselor osr staff member and a confirmation receipt is received. & Verifies the camp staff member receives a parent's message via email. \vspace*{1em}\\	\hline
	TC02-03 & In-app messaging & In-app messaging message is received by counselor or staff member and a confirmation receipt is received. & Verifies the camp staff member.\vspace*{1em}\\\hline
\end{longtable}
\end{center}
\clearpage


%------------------------------------
% Megan's Test Cases
%------------------------------------
\subsection*{Test Suite 2: View Camper Information}

\begin{table}[H]
\begin{center}
\caption{TC03}
\label{TC03}
\begin{tabular}{p{0.20\linewidth}p{0.70\linewidth}}
	ID: & TC03\\\hline
	Name: & Search Campers Test \\\hline
	Author: & Megan Steinmasel\\\hline
	Summary: & Given the search functionality in the system, it must be searchable for any components that make up a campers or parents name, returning entries that are related. \\\hline
	Related \hspace{5em} Requirements:& Search Campers (\cref{des:search campers}); \hyperlink{Req2}{Req 2}, \hyperlink{Req4}{Req 4}\\\hline
	Preconditions:& \begin{enumerate}[topsep=0pt]
		\item Camper and parent information is submitted into the system.
		\item Camper and parent information is accessible from search.
	\end{enumerate}\\\hline
	Test Script/ Procedure: & \begin{enumerate}[topsep=0pt]
	\item Navigate to search option.
	\item Enter search term (this is defined per test) into search bar.
	\item Click enter.
	\end{enumerate}\\\hline
	Test Data & Camper: ``Max Johnson" with Parent: ``Jane Williams".
\end{tabular}
\end{center}
\end{table}

\begin{center}
\begin{longtable}{|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|}
	\hline 
	Test Case \# & Test Data & Expected Result & Summary\\\hline
	TC03-01 & Camper first name: ``Max" & Relevant camper is displayed & Verifies a valid camper's first name is searchable and their information is displayed correctly.\vspace*{1em}\\\hline
	TC03-02 & Camper last name: ``Johnson" & Relevant camper is displayed & Verifies a valid camper's last name is searchable and their information is displayed correctly.\vspace*{1em}\\	\hline
	TC03-03 & Camper first and last name: ``Max Johnson" & Relevant camper is displayed & Verifies a valid camper's first and last name is searchable and their information is displayed correctly.\vspace*{1em}\\\hline
	TC03-04 & Parent first name: ``Jane" & Relevant parent is displayed & Verifies a valid parent's first name is searchable and their information is displayed correctly.\vspace*{1em}\\\hline
	TC03-05 & Parent last name: ``Williams" & Relevant parent is displayed & Verifies a valid parent's last name is searchable and their information is displayed correctly.\vspace*{1em}\\\hline
	TC03-06 & Camper first and last name: ``Jane Williams" & Relevant parent is displayed & Verifies a valid parent's first and last name is searchable and their information is displayed correctly.\vspace*{1em}\\\hline
	TC03-07 & First name: ``ffjbvl" & No campers/parents are displayed & Verifies an invalid first name displays no result.\vspace*{1em}\\\hline
	TC03-08 & Last name: ``cfgkp" & No campers/parents are displayed & Verifies an invalid last name displays no result.\vspace*{1em}\\\hline
	TC03-09 & First and last name: ``ffjbvl cfgkp" & No campers/parents are displayed & Verifies an invalid first or last name displays no result.\\\hline
\end{longtable}
\end{center}
\clearpage


\begin{table}[H]
\begin{center}
\caption{TC04}
\label{TC04}
\begin{tabular}{p{0.20\linewidth}p{0.70\linewidth}}
	ID: & TC04\\\hline
	Name: & Sort Campers \\\hline
	Author: & Megan Steinmasel\\\hline
	Summary: & Given the sorting functionality in the system, it must be diviable for any components that make up a camper's characteristics: name, allergies, camp attending, payment/account balance, age. \\\hline
	Related \hspace{5em} Requirements:& Sort Campers (\cref{des:sort campers}); \hyperlink{Req3}{Req 3}, \hyperlink{Req4}{Req 4}\\\hline
	Preconditions:& \begin{enumerate}[topsep=0pt] 
		\item Camper and parent information (name, allergies, camp, account balance, age) is submitted into the system.
		\item Camper and parent information is accessible for sorting.
	\end{enumerate}\\\hline
	Test Script/ Procedure: & \begin{enumerate}[topsep=0pt]
	\item Navigate to sort option.
	\item Select a category of camper information to sort by.
	\item Click enter.
	\end{enumerate}\\\hline
	Test Data & \vspace*{.25em} A full dichotomy of the following character sets (324 entries total): \newline
	\hspace*{1cm} name $\rightarrow$ $\{$Alex Doe, Alex Smith$\}$	\newline
	\hspace*{1cm} allergies $\rightarrow$ $\{$None, peanuts, gluten, misc$\}$	\newline
	\hspace*{1cm} camp $\rightarrow$ $\{$Camp 1, Camp 2, Camp 3$\}$\newline
	\hspace*{1cm} account balance $\rightarrow$ $\{$\$0, \$0.12, \$10$\}$\newline
	\hspace*{1cm} age $\rightarrow$ $\{$7, 12, 17$\}$
\end{tabular}
\end{center}
\end{table}


\begin{center}
\begin{longtable}{|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|}
	\hline
	Test Case \# & Sort Category & Expected Result & Summary\\\hline
	TC04-01 & Name & Campers are sorted alpha-numerically by name & Verifies sorting is valid and completed for the name category.\vspace*{1em}\\\hline
	TC04-02 & Allergies & Campers are sorted alpha-numerically by allergies & Verifies sorting is valid and completed for the allergies category.\vspace*{1em}\\	\hline
	TC04-03 & Camp & Campers are sorted alpha-numerically by camp & Verifies sorting is valid and completed for the camp category.\vspace*{1em}\\\hline
	TC04-04 & Account Balance & Campers are sorted numerically by payments & Verifies sorting is valid and completed for the payments category.\vspace*{1em}\\\hline
	TC04-05 & Age & Campers are sorted numerically by age & Verifies sorting is valid and completed for the age category.\vspace*{1em}\\\hline
\end{longtable}
\end{center}
\clearpage


%------------------------------------
% Will's Test Cases
%------------------------------------
\subsection*{Test Suite 3: Schedule}

\begin{table}[H]
\begin{center}
\caption{TC05}
\label{TC05}
\begin{tabular}{p{0.20\linewidth}p{0.70\linewidth}}
	ID: & TC05\\\hline
	Name: & View Counselor Schedule \\\hline
	Author: & William Jardee\\\hline
	Summary: & Each counselor must be able to view their own schedule according to a given input of dates. This needs to be robust to any weird combination of dates and times requested and worked in the system. \\\hline
	Related \hspace{5em} Requirements:& View Counselor Schedules (\cref{des:view counselor schedules}); \hyperlink{Req3}{Req 3}\\\hline
	Preconditions:& \begin{enumerate}[topsep=0pt]
		\item Request for counself schedules ifs valid at this time (i.e., necessary credentials have been tested).
		\item Counselor schedules have been generated in the system. 
	\end{enumerate}\\\hline
	Test Script/ Procedure: & \begin{enumerate}[topsep=0pt]
		\item Sign in as appropriate user (counselor).
		\item Navigate to ``schedules" page.
		\item Enter appropriate data (dates).
		\item Click enter.
	\end{enumerate}\\\hline
	Test Data & \vspace*{.25em} Two counselor's data:
	\begin{itemize}[topsep=0pt]
		\item Andrew: Works this week Monday-Wednesday 9am-3:30pm and Thursday 10am-4pm. Does not work next week.
		\item Bailey: Works this week Wednesday 9pm-Thursday 10:30am and saturday-Tuesday 7am-5pm.
	\end{itemize}
\end{tabular}
\end{center}
\end{table}

\begin{center}
\begin{longtable}{|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|}
	\hline 
	Test Case \# & Messaging System & Expected Result & Summary\\\hline
	TC05-01 & Andrew: Monday of this week $\longrightarrow$ Friday of this week. & Weekly schedule view displayed. & Verifies that the counselor's data is seen individually, only the dates of interest are shown, and the appropriate times are shown. \vspace*{1em}\\\hline
	TC05-02 & Andrew: Monday of next week $\longrightarrow$ Friday of next week. & Weekly schedule view displayed. It should be empty. & Verifies weeks are separate and empty weeks are viewable. \vspace*{1em}\\\hline
	TC05-03 & Andrew: Wednesday this week $\longrightarrow$ Wednesday this week. & A single-day version of schedule view displayed. & Verifies single-day querry recognized. Slightly different visualization of single-day.\vspace*{1em}\\\hline
	TC05-04 & Andrew: Wednesday of this week $\longrightarrow$ Wednesday of next week. & Weekly schedule view displayed. & Verifies querry can be started on arbitrary day and split over weekend.\vspace*{1em}\\\hline
	TC05-05 & Bailey: Monday of this week $\longrightarrow$ Friday of this week. & Weekly schedule view displayed. & Verifies counselor schedules are seen differently. checks that work day can be split over midnight.\vspace*{1em}\\\hline
	TC05-06 & Bailey: Wednesday of this week $\longrightarrow$ Wednesday of next week. & Weekly schedule view is displayed. & Verifies query can be started on arbitrary day and split over weekend; in case of different counselors.\vspace*{1em}\\\hline
	TC05-07 & Bailey: Monday of this week $\longrightarrow$ Tuesday of this week. & Weekly schedule view displaeyed. It should be empty. & Verifies days before first workday are viewable. \vspace*{1em}\\\hline
	TC05-08 & Andrew: Friday of this week $\longrightarrow$ Monday of this week. & Error Message displayed: second date must be after first date. & Verifies system checks that range cannot be backwards.\vspace*{1em}\\\hline
	TC05-09 & Andrew: Monday of next week $\longrightarrow$ Fiday of this week. & Error Message displayed: second date must be after first date. & Verifies system checks that range cannot be backwards (checks date, not weekday name).\vspace*{1em}\\\hline
	TC05-10 & Andrew: Montday of this week $\longrightarrow$ Friday of next week. Then, request a refresh of the page. & Weekly schedule view is displayed (of the correct two week period). & Verifies query is preserved over refresh.\vspace*{1em}\\\hline
\end{longtable}
\end{center}
\clearpage


\begin{table}[H]
\begin{center}
\caption{TC06}
\label{TC06}
\begin{tabular}{p{0.20\linewidth}p{0.70\linewidth}}
	ID: & TC06\\\hline
	Name: & View Camper Schedules from Parent(s) View \\\hline
	Author: & William Jardee\\\hline
	Summary: & Parents need to be able to view a schedule that leverages the predictable schedule structure and thus is easy to understand. \\\hline
	Related \hspace{5em} & View Camper Schedules from Parent(s) View (\cref{des:view camper schedules}); \hyperlink{Req3}{Req 3}\\\hline
	Preconditions:& \begin{enumerate}[topsep=0pt] 
		\item Parents must be logged in.
		\item Parents must have children registered as campers.
	\end{enumerate}\\\hline
	Test Script/ Procedure: & \begin{enumerate}[topsep=0pt]
		\item Sign in as appropriate user (parent).
		\item Navigate to ``schedule" page.
		\item Enter appropriate data (choose a week from the drop-down menu; it should be labeled by the dates of the week).
		\item Click enter.
	\end{enumerate}\\\hline
	Test Data & \vspace*{.25em} Three parents' data:
	\begin{itemize}[topsep=0pt]
		\item Alex: Has one child who will be attending this week's camps.
		\item Braden: Has two childre. child 1 had camp last week and has camp this week. Child 2 has bamp this week and next week.
		\item Cathy: Has one child who will be attending this week's camp and camp in two weeks.
		\item Dana: Does not have any children atending any upcoming camps; however, his data is on the record from previous camps.
	\end{itemize}
\end{tabular}
\end{center}
\end{table}

\begin{center}
\begin{longtable}{|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|}
	\hline
	Test Case \# & Messaging System & Expected Result & Summary\\\hline
	TC06-01 & Alex; this week. & Weekly schedule for \textit{their} child view displayed. & Verifies the standard display case.\vspace*{1em}\\\hline
	TC06-02 & Alex; next week. & Prompt an error tht ehy do not have a child attending camp next week. Presents next week child will be attending (this week). & Verifies system checks for invalid search. \vspace*{1em}\\\hline
	TC06-03 & Alex; this week $\longrightarrow$ next week. & Notify that their child will not be attending next week. display two-week schedule for camper. & Verifies system checks for notification and rending empty weeks.\vspace*{1em}\\\hline
	TC06-04 & Alex; last week. & Promp an error that they did not have a child attending last week. & Verifies can query previous weeks.\vspace*{1em}\\\hline
	TC06-05 & Braden; this week. & Weekly scheudle for their children shown, shown in parallel view as separate schedules. & Verifies multiple-child case.\vspace*{1em}\\\hline
	TC06-06 & Braden; next week. & Weekly schedule for only child 2. & Verifies correctly separates children and only shows relevant information.\vspace*{1em}\\\hline
	TC06-07 & Braden; this week $\longrightarrow$ next week & Weekly schedule for both children, shown in parallel as separate schedules. & Verifies that multiple children can be searched when empty space is present.\vspace*{1em}\\\hline
	TC06-08 & Braden; last week. & Weekly schedule for only child 1. & Verifies searching previous weeks with multiple children.\vspace*{1em}\\\hline
	TC06-09 & Cathy; this week $\longrightarrow$ week after next. & Notify that child will not be attending next week. Displays three-week view. & Verifies parsing gap in schedule.\vspace*{1em}\\\hline
	TC06-10 & Dana; this week. & Notify that their child will not be attending next week. Presents next week child will be attending $\rightarrow$ not registerd for upcoming camps, so offers link to sign up fro camp. & Verifies empty state and unique prompt to register for a camp.\vspace*{1em}\\\hline
\end{longtable}
\end{center}
\clearpage


%------------------------------------
% Jacob's Test Cases
%------------------------------------
\subsection*{Test Suite 4: Attendance Tracking}

\begin{table}[H]
\begin{center}
\caption{TC07}
\label{TC07}
\begin{tabular}{p{0.20\linewidth}p{0.70\linewidth}}
	ID: & TC07\\\hline
	Name: & Track Attendance \\\hline
	Author: & Jacob Coleman\\\hline
	Summary: & Counselors have the ability to update camper's attendance, and can't edit those who aren't in the system/on their schedule. \\\hline
	Related \hspace{5em} & Track Attendance (\cref{des:track attendance}); \hyperlink{Req1}{Req 1}\\\hline
	Preconditions:& \begin{enumerate}[topsep=0pt] 
		\item Camper has been entered into the system.
		\item Camper is able to be searched for in system.
	\end{enumerate}\\\hline
	Test Script/ Procedure: & \begin{enumerate}[topsep=0pt]
		\item Sign in with proper credentials.
		\item Navigate to attendance page.
		\item Enter appropriate data.
		\item Click enter.
	\end{enumerate}\\\hline
	Test Data & \vspace*{.25em} Two camper's data:
	\begin{itemize}[topsep=0pt]
		\item John Doe: Camper who is currently present.
		\item Jimmy Smith: Camper who is currently absent.
	\end{itemize}
\end{tabular}
\end{center}
\end{table}

\begin{center}
\begin{longtable}{|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|}
	\hline
	Test Case \# & Search Term & Expected Result & Summary\\\hline
	TC07-01 & Enter camper name: ``John Doe" & Notification that the camper is marked as present. & Verifies that the camper name entered has been acounted for and registered as ``present" in the system.\vspace*{1em}\\\hline
	TC07-02 & Enter camper name: ``Jimmy Smith" & Notification that the camper is marked as absent& Verifies the camper name entered has not been accounted for, being marked as ``absent" in the system.\vspace*{1em}\\	\hline
	TC07-03 & Enter camper name: ``Mike Jones" & Notified that the camper is not registered in the system & Verifies the camper exists in the registered list of campers. \vspace*{1em}\\\hline
\end{longtable}
\end{center}
\clearpage


\begin{table}[H]
\begin{center}
\caption{TC08}
\label{TC08}
\begin{tabular}{p{0.20\linewidth}p{0.70\linewidth}}
	ID: & TC08\\\hline
	Name: & Schedule Absence \\\hline
	Author: & Jacob Coleman\\\hline
	Summary: & Parents can modify their camper's schedule fully automatically without need to contact any personal. \\\hline
	Related \hspace{5em} Requirements:& Schedule Absence (\cref{des:schedule absence}); \hyperlink{Req1}{Req 1}\\\hline
	Preconditions:& \begin{enumerate}[topsep=0pt] 
		\item Parent is logged in.
		\item Parent has at least one child registered as a camper.
	\end{enumerate}\\\hline
	Test Script/ Procedure: & \begin{enumerate}[topsep=0pt]
	\item navigate to ``schedules" page.
	\item Select to input excused absence.
	\item Enter appropriate data (select date(s) for absence).
	\item Click enter.
	\end{enumerate}\\\hline
	Test Data & \vspace*{.25em} Two family's data:
	\begin{itemize}[topsep=0pt]
		\item Family 1: Has one child attending camp this week and next (Jimmy Smith).
		\item Family 2: Has two children attending camp this week (John Doe and Jane Doe).
		\item Family 3: Has one child attending camp next week (Joseph Williams).
	\end{itemize}
\end{tabular}
\end{center}
\end{table}

\begin{center}
\begin{longtable}{|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|p{0.22\linewidth}|}
	\hline
	Test Case \# & Search Term & Expected Result & Summary\\\hline
	TC08-01 & Family 1; Jimmy will be absent today. & Jimmy is excused from camp for current day; message is sent to camp. & Verifies that the system is updated that the camper will be absent from camp today.\vspace*{1em}\\\hline
	TC08-02 & Family 1; Jimmy will be absent tomorrow. & Jimmy is excused from camp for tomorrow. & Verifies that the system is updated that the camper will be absent from camp tomorrow.\vspace*{1em}\\	\hline
	TC08-03 & Family 2; John will be absent today & Excuses camper of same family dataset from camp today; message is sent to camp. & Verifies that a single child of a family can be excused.\vspace*{1em}\\\hline
	TC08-04 & Family 2; John and Jane will be absent today & Excuse both campers of same family dataset from camp today; message is sent to camp. & Verifies that a all child of a family can be excused.\vspace*{1em}\\\hline
	TC08-05 & Family 2; John will be absent today and Jane will be absent tomorrow & Excuse both campers of same family dataset from camp on different days; message is sent to camp. & Verifies that a all child of a family can be excused, and those days can be different.\vspace*{1em}\\\hline
	TC08-06 & Family 1; Jimmy will be absent tomorrow -> week from today & Excuse campers from camp over this range; message is sent to camp. & Verifies camper can be excused over a range.\vspace*{1em}\\\hline\
	TC08-07 & Family 3; Joseph will be absent today & Parent is notified that the camper is not scheduled for camp today and nothing is changed in the system. & Verifies campers cannot be marked absent when not attending.\vspace*{1em}\\\hline
\end{longtable}
\end{center}

\clearpage


%------------------------------------
% Appendix of source
%------------------------------------

\appendix
\section{Camp Management System}\label{appendix:camp_sys}
To make cross referencing easier, the used requirement and usecases from the original ``Camp Management System Requirements Spec" have been copied here. Any hyperlinks will redirect you to the relevant requirements/usecase.

\subsection{Requirements}

\noindent\textit{\hypertarget{Req1}{Requirement 1}}: A way to track attendance.\vspace{0.5em}

\noindent\textit{\hypertarget{Req2}{Requirement 2}}: View Camper information.\vspace{0.5em}

\noindent\textit{\hypertarget{Req3}{Requirement 3}}: Create and view schedule.\vspace{0.5em}

\noindent\textit{\hypertarget{Req4}{Requirement 4}}: Send a message to parents.\vspace{0.5em}

\subsection{Use Cases}
% Test Suite 1:  Messaging System

\begin{table}[!htb]
\caption{Usecase 1}
\label{des:message camp}	
\begin{center}
\begin{tabular}{p{0.30\linewidth}p{0.60\linewidth}}
	Name: & Message Camp\\\hline
	Description: & The parent send a message to a counselor or staff members.\\\hline
	Related Requirements:& \hyperlink{Req4}{Req 4}\\\hline
	Preconditions:& The parent has contact information in the system.\\\hline
	Successful end condition:& Staff receives a message from parent.\\\hline
	Failed end condition:& Message not received. \\\hline
	Actors:& Counselor, Parent.\\\hline
	Basic Flow of Events: & \begin{enumerate}[topsep=0pt]
		\item Message is created.
		\item The message is sent.
		\item confirmation receipt is sent.
	\end{enumerate}\\\hline
	Extensions/Exceptional Flow of Events: & \vspace*{.25em}  N/A
\end{tabular}
\end{center}
\end{table}


\begin{table}[!htb]
\caption{Usecase 2}
\label{des:message parent}
\begin{center}
\begin{tabular}{p{0.30\linewidth}p{0.60\linewidth}}
	Name: & Message Parent\\\hline
	Description: & A counselor or staff member sends a message to a parent.\\\hline
	Related Requirements:& \hyperlink{Req4}{Req 4}\\\hline
	Preconditions:& The parent has contact information or has created a profile.\\\hline
	Successful end condition:& The parent receives a message.\\\hline
	Failed end condition:& Message not received or an account is not found.. \\\hline
	Actors:& Counselor, Parent.\\\hline
	Basic Flow of Events: & \begin{enumerate}[topsep=0pt]
		\item The message is created.
		\item Type of the message is chosen (text, email, or in-app messaging).
		\item The message is sent.
		\item A confirmation receipt is sent.
	\end{enumerate}\\\hline
	Extensions/Exceptional Flow of Events: & \vspace*{.25em}  N/A
\end{tabular}
\end{center}
\end{table}

% Test Suite 2: View camper information

\begin{table}[!htb]
\caption{Usecase 3}
\label{des:search campers}
\begin{center}
\begin{tabular}{p{0.30\linewidth}p{0.60\linewidth}}
	Name: & Search Campers \\\hline
	Description: & Look up campers by name or parent name. \\\hline
	Related Requirements:& \hyperlink{Req2}{Req 2}, \hyperlink{Req4}{Req 4}\\\hline
	Preconditions:& All Camper information is accessible by councelors.\\\hline
	Successful end condition:& Relevant camper(s) are displayed based on search terms.\\\hline
	Failed end condition:& Not all relevant campers appear from search term.\\\hline
	Actors:& Counselor.\\\hline
	Basic Flow of Events: & \begin{enumerate}[topsep=0pt]
		\item Counselor enters search term.
		\item System searches camper list for term.
		\item System displays results to counselor.
	\end{enumerate}\\\hline
	Extensions/Exceptional Flow of Events: & \begin{enumerate}[topsep=0pt]
		\item No results found based on term.
		\item System tells user there are no results for the term.	
	\end{enumerate}
\end{tabular}
\end{center}
\end{table}

\begin{table}[!htb]
\caption{Usecase 4}
\label{des:sort campers}
\begin{center}
\begin{tabular}{p{0.30\linewidth}p{0.60\linewidth}}
	Name: & Sort Campers.\\\hline
	Description: & Sort the campers in the database alpha-numerically by name, allergies, camp, payments, or age.\\\hline
	Related Requirements:& \hyperlink{Req3}{Req 3}, \hyperlink{Req4}{Req 4}\\\hline
	Preconditions:& All camper information is accessibly by counselors.\\\hline
	Successful end condition:& Campers are sorted by specified category.\\\hline
	Failed end condition:& Sorting is not displayed corrrectly based on selected category.\\\hline
	Actors:& Counselor,\\\hline
	Basic Flow of Events: & \begin{enumerate}[topsep=0pt]
		\item Counselor selects category to sort.
		\item System sorts campers by category.
		\item System displays sorted results to counselor.
	\end{enumerate}\\\hline
	Extensions/Exceptional Flow of Events: & \vspace*{.25em}  N/A
\end{tabular}
\end{center}
\end{table}

% Test Suite 3: Schedule

\begin{table}[!htb]
\caption{Usecase 5}
\label{des:view counselor schedules}
\begin{center}
\begin{tabular}{p{0.30\linewidth}p{0.60\linewidth}}
	Name: & View Counselor Schedule\\\hline
	Description: & Show a counselor their activities on their schedule.\\\hline
	Related Requirements:& \hyperlink{Req3}{Req 3}\\\hline
	Preconditions:& Counselor must be logged in.\\\hline
	Successful end condition:& Counselor views their schedule. \\\hline
	Failed end condition:& \\\hline
	Actors:& Counselor. \\\hline
	Basic Flow of Events: & \begin{enumerate}[topsep=0pt]
		\item Counselor Chooses to view schedule.
		\item System displays the counselor's schedule.
	\end{enumerate}\\\hline
	Extensions/Exceptional Flow of Events: & \vspace*{.25em}  N/A
\end{tabular}
\end{center}
\end{table}

\begin{table}[!htb]
\caption{Usecase 6}
\label{des:view camper schedules}
\begin{center}
\begin{tabular}{p{0.30\linewidth}p{0.60\linewidth}}
	Name: & View Camper Schedule(s) from Parent View.\\\hline
	Description: & Parent's must be able to view their camper's schedule or schedules if they have multiple children attending.\\\hline
	Related Requirements:& \hyperlink{Req3}{Req 3}\\\hline
	Preconditions:& Parents must be logged in and have children registered as campers.\\\hline
	Successful end condition:& Parent view schedule(s) \\\hline
	Failed end condition:& \\\hline
	Actors:& Counselor. \\\hline
	Basic Flow of Events: & \begin{enumerate}[topsep=0pt]
		\item Parent chooses to view schedule.
		\item System displays the parent's schedule.
	\end{enumerate}\\\hline
	Extensions/Exceptional Flow of Events: & \vspace*{.25em}  N/A
\end{tabular}
\end{center}
\end{table}

% Test Suite 4: Attendance Tracking

\begin{table}[!htb]
\caption{Usecase 7}
\label{des:track attendance}
\begin{center}
\begin{tabular}{p{0.30\linewidth}p{0.60\linewidth}}
	Name: & Track Attendance\\\hline
	Description: & Track campers attendance everyday.\\\hline
	Related Requirements:& \hyperlink{Req1}{Req 1}\\\hline
	Preconditions:& Camper is in the system.\\\hline
	Successful end condition:& Attendance successfully marked. \\\hline
	Failed end condition:& Attendance not added.\\\hline
	Actors:& Counselor. \\\hline
	Basic Flow of Events: & \begin{enumerate}[topsep=0pt]
		\item Camper shows up or does not show up.
		\item Counselor marks whether or not they showed up in the attendance database.
	\end{enumerate}\\\hline
	Extensions/Exceptional Flow of Events: & \vspace*{.25em}  N/A
\end{tabular}
\end{center}
\end{table}

\begin{table}[!htb]
\caption{Usecase 8}
\label{des:schedule absence}
\begin{center}
\begin{tabular}{p{0.30\linewidth}p{0.60\linewidth}}
	Name: & Schedule absence.\\\hline
	Description: & Parents are able to schedule a camper's absence ahead of time. For example, if a camper has a dentist appointment in two days, then the parents can schedule the absence early. Absences can typeically be multiple days in advance..\\\hline
	Related Requirements:& \hyperlink{Req1}{Req 1}\\\hline
	Preconditions:& Camper is in the system.\\\hline
	Successful end condition:& Counselors are aware that the camper will not show up that day. \\\hline
	Failed end condition:& Camper marked unexcused.\\\hline
	Actors:& Parent. \\\hline
	Basic Flow of Events: & \begin{enumerate}[topsep=0pt]
		\item Parent logs into the system.
		\item Parent chedules camper's absence.
	\end{enumerate}\\\hline
	Extensions/Exceptional Flow of Events: & \vspace*{.25em}  N/A
\end{tabular}
\end{center}
\end{table}

%Empty example of use case table.


%\begin{table}[!htb]
%\begin{center}
%\begin{tabular}{p{0.30\linewidth}p{0.60\linewidth}}
%	Name: & \\\hline
%	Description: & \\\hline
%	Related Requirements:& \\\hline
%	Preconditions:& \\\hline
%	Successful end condition:& \\\hline
%	Failed end condition:& \\\hline
%	Actors:& \\\hline
%	Basic Flow of Events: & \begin{enumerate}[topsep=0pt]
%		\item $\cdot$
%	\end{enumerate}\\\hline
%	Extensions/Exceptional Flow of Events: & \vspace*{.25em}  N/A
%\end{tabular}
%\label{des:}	
%\end{center}
%\end{table}


\end{document}
